Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-07-10 patchy-selection-paper.tex
small change to discussion/ack

\paragraph{Other patch geometries}
We have studied circular patches of habitat at long distances from each other.
Real habitat geometry can be much more complex,
e.g.\ with archipelagos of patches of varying sizes, 
or patches connected by long, skinny corridors, for instance.
The work of \citet{cantrell1991diffusive} comes closest to a general theory of balanced polymorphisms in such habitats.
It is possible that our techniques could be applied in their much more general setting,
as both are based, fundamentally, on branching process approximations.

@@

\subsection*{Acknowledgements}
We would like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd and the rest of the Coop lab for helpful comments on the manuscript.

>>>>

\paragraph{Other geographic models}
We have studied circular patches of habitat at long distances from each other.
Real habitat geometry can be much more complex,
e.g.\ with archipelagos of patches of varying sizes, 
or patches connected by long, skinny corridors, for instance.
The work of \citet{cantrell1991diffusive} comes closest to a general theory of balanced polymorphisms in such habitats.
It is possible that our techniques could be applied in their much more general setting,
as both are based, fundamentally, on branching process approximations.
It is also interesting to think about the probability of convergent
adaptation to continuously varying environments, e.g. replicated
environmental clines.

@@

\subsection*{Acknowledgements}
We would like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.
